Scattering of massless particles: scalars, gluons and gravitons

### 2024-07-09 test/main.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[CHY formula]{Scattering of massless particles: scalars, gluons and gravitons}
\subtitle{Freddy Cachazo, Song He, Ellis Ye Yuan}
\author{Su Yingze}
\institute{Nagoya University}
\date[7 23rd 2024]{July 23rd 2024} 
\begin{document}
\frame{\titlepage}

\section{Why the S-matrix is so important?}
\iffalse
\begin{frame}
    It is well known that in the conventional quantum field theory, S-matrix is a deduced physical quantity following
    unitarity and localty. But as the understanding of scatering amplitudes improves, by using the amplituhedron method,
    S-matrix can be constructed directly from a special kind of geometry object and we even have no need to introduce the Lagrangian
    of the specific theory. Also the localty and unitarity can be the outcome from the request of positivity instead of input or previous constraints.
    It may give us some implications about the significance of S-matrix and encourage us to reconstruct the field theory in another way.
    Most of the developments before have made for particular theories like $\mathcal{N}=4$ Super Yang-Mills theory or $\mathcal{N}=8$ Supergravity,
    but this paper gives some hints to the construction of amplitudes for theories with less or no supersymmetry.
\end{frame}
\fi
\begin{frame}{}
    \frametitle{Some developments of amplitudes}
    \begin{itemize}
        \item BCFW recursion relation.
        \begin{equation*}
            \!\!\!\!A_n ~= \!\!\!\!\sum_{\text{diagrams}~I} \hat{A}_\text{L}(z_I) 
            \,\frac{1}{P_I^2}\,
            \hat{A}_\text{R}(z_I)
               ~~=
               \!\!\!\!\sum_{\text{diagrams}~I}
           \raisebox{-5.5mm}{\includegraphics[height=1.4cm]{recrel1.pdf}}
           \,.
        \end{equation*}
        \item Dual superconformal symmetry of $\mathcal{N}=4$ Super Yang-Mills amplitude.
        \item Generalized unitarity
        \item Positive geometry and Amplituhedra.
        \item \dots
    \end{itemize}
    \begin{figure}
        \centering
        \includegraphics[width=0.25\linewidth]{Grassmannian.png}
        \caption{Positive Grassmanian}
    \end{figure}
\end{frame}
\section{Review of some pertinent results}
\begin{frame}{Gauge theory color structure}
    At tree level, with particles in the adjoint representaion of gauge group SU(N), the amplitude can be 
decomposed as
\textcolor{red}{\begin{equation*}
    \mathcal{A}_n^{tree}(1,2,3,\dots,n)=\sum _{\mathcal{P}(2,3,\dots,n)}Tr[T^{a_1}T^{a_2}T^{a_3}\dots
    T^{a_n}]A_n^{tree}[1,2,3,\dots,n]
\end{equation*}}

@@

\section{CHY Formula}
\begin{frame}{Scattering equations}
    It has benn proposed that there is connection between the scattering data of n massless particles and the n-punctured sphere from a rational map
    \begin{equation*}
        k_\mu^a=\frac{1}{2\pi i}\oint_{|z-\sigma_a|}dz\frac{p^\mu(z)}{\prod ^n_{b=1}(z-\sigma_b)}
    \end{equation*}

@@

    \begin{block}{\textcolor{red}{Scattering equations}}
        \begin{equation*}
            \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\qquad a\in \{1,\dots,n\}
        \end{equation*}
    \end{block}
    It has been proved that the number of solutions in any dimension is $\alert{(n-3)!}$, and only \alert{$n-3$} of the equtions are independent, so we can rewrite the scattering equations as following 
    \begin{equation*}
        \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\quad a\in \{4,5,\dots,n\}\quad and\quad  \sigma_1\rightarrow\infty,\sigma_2=0,\sigma_3=1
    \end{equation*}
\end{frame}
\iffalse
\begin{frame}{KLT Relation}
    So-called KLT relation, in the language of field theory, refers to the decomposition of \alert{gravity amplitudes} to \alert{two gauge theory amplitues}. 
    \begin{table}[]
        \resizebox{\textwidth}{!}{
        \begin{tabular}{|l|l|l|l|l|}
        \hline
         \(\mathcal{N}\) & Factors & Supergravity   \\ \hline
         8 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=4SYM\)      &   pure \(\mathcal{N}=8 \)SG             \\ \hline
         6 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=2SYM\)      &   pure \(\mathcal{N}=6 \)SG             \\ \hline
         5 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=1SYM\)      &   pure \(\mathcal{N}=5 \)SG             \\ \hline
         4 &   \(\mathcal{N}=4SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=4 \)SG,\(n_\nu\)vector multiplets             \\ \hline
         4 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=2SYM\)      &    \(\mathcal{N}=4 \)SG,2 vector multiplets            \\ \hline
         3 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=1SYM\)      &    \(\mathcal{N}=3 \)SG,1 vector multiplet           \\ \hline
         2 &   \(\mathcal{N}=2SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=2 \)SG,\(n_\nu\) multiplets+1 vector multiplets            \\ \hline
         2 &   \(\mathcal{N}=1SYM\otimes \mathcal{N}=1SYM\)       &    \(\mathcal{N}=2 \)SG ,1 hypermultiplet               \\ \hline
         1 &   \(\mathcal{N}=1SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &     \(\mathcal{N}=1 \)SG,  \(n_\nu\) vector and 1 chiral multiplet           \\ \hline
        \end{tabular}
        }
        \end{table}
\end{frame}
\fi
\begin{frame}{KLT Orthogonality}
    $\bullet$ KLT orthogonality is a striking property of the solutions to scattering equations.
    \begin{block}{Proposition 1}
        \begin{equation*}
            \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\delta_{ij}
        \end{equation*}
    \end{block}

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[CHY formula]{Scattering of massless particles: scalars, gluons and gravitons}
\subtitle{Freddy Cachazo, Song He, Ellis Ye Yuan}
\author{Su Yingze}
\institute{Nagoya University}
\date[7 23rd 2024]{July 23rd 2024} 
\begin{document}
\frame{\titlepage}

\section{Why the S-matrix is so important?}
\iffalse
\begin{frame}
    It is well known that in the conventional quantum field theory, S-matrix is a deduced physical quantity following
    unitarity and localty. But as the understanding of scatering amplitudes improves, by using the amplituhedron method,
    S-matrix can be constructed directly from a special kind of geometry object and we even have no need to introduce the Lagrangian
    of the specific theory. Also the localty and unitarity can be the outcome from the request of positivity instead of input or previous constraints.
    It may give us some implications about the significance of S-matrix and encourage us to reconstruct the field theory in another way.
    Most of the developments before have made for particular theories like $\mathcal{N}=4$ Super Yang-Mills theory or $\mathcal{N}=8$ Supergravity,
    but this paper gives some hints to the construction of amplitudes for theories with less or no supersymmetry.
\end{frame}
\fi
\begin{frame}{}
    \frametitle{Some developments of amplitudes}
    \begin{itemize}
        \item BCFW recursion relation.
        \begin{equation*}
            \!\!\!\!A_n ~= \!\!\!\!\sum_{\text{diagrams}~I} \hat{A}_\text{L}(z_I) 
            \,\frac{1}{P_I^2}\,
            \hat{A}_\text{R}(z_I)
               ~~=
               \!\!\!\!\sum_{\text{diagrams}~I}
           \raisebox{-5.5mm}{\includegraphics[height=1.4cm]{recrel1.pdf}}
           \,.
        \end{equation*}
        \item Dual superconformal symmetry of $\mathcal{N}=4$ Super Yang-Mills amplitude.
        \item Generalized unitarity
        \item Positive geometry and Amplituhedra.
        \item \dots
    \end{itemize}
    \begin{figure}
        \centering
        \includegraphics[width=0.25\linewidth]{Grassmannian.png}
        \caption{Positive Grassmanian}
    \end{figure}
\end{frame}
\begin{frame}

%Straight Lines [id:da04992460244937069] 
\draw    (116,79) -- (116.49,163) ;
\draw [shift={(116.5,165)}, rotate = 269.67] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da7393833245286348] 
\draw    (218,134) -- (343.5,134) ;
\draw [shift={(345.5,134)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da6514784763465036] 
\draw    (447,76) -- (447.49,160) ;
\draw [shift={(447.5,162)}, rotate = 269.67] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da8109804852164224] 
\draw    (257,265) -- (320.5,265) ;
\draw [shift={(322.5,265)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

% Text Node
\draw (79,46) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\mathrm{Lagrangian}$};
% Text Node
\draw (86,178) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\mathrm{S-matrix}$};
% Text Node
\draw (391,49.4) node [anchor=north west][inner sep=0.75pt]    {$\mathrm{Amplituhedron}$};
% Text Node
\draw (417,173) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\mathrm{S-matrix}$};
% Text Node
\draw (94,256) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\mathrm{Positivity}$ of $\mathrm{geometry}$ };
% Text Node
\draw (339,255) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\mathrm{Unitarity}$ and $\mathrm{Localty}$};

\end{frame}
\iffalse
\section{Review of some pertinent results}
\begin{frame}{Gauge theory color structure}
    At tree level, with particles in the adjoint representaion of gauge group SU(N), the amplitude can be 
decomposed as
\textcolor{red}{\begin{equation*}
    \mathcal{A}_n^{tree}(1,2,3,\dots,n)=\sum _{\mathcal{P}(2,3,\dots,n)}Tr[T^{a_1}T^{a_2}T^{a_3}\dots
    T^{a_n}]A_n^{tree}[1,2,3,\dots,n]
\end{equation*}}

@@

\fi
\section{CHY Formula}
    \frametitle{Motivation}
    %Most of the developments of amplitudes before have made for some specific theories, like N=4 super yang-mills theory and N=8 supergravity.
    %The natural question is that what is the space of all field theories whose tree level S-matrix can be expressed in a compact form? 
        \item Compact form of amplitudes for sclar, pure Yang-Mills and gravity theories in any spacetime dimension.
        %The author introduce a compact form of tree level amplitudes for three different theories, colored scalar theory, pure Yang-Mills and Einstein gravity.
        %The concrete form of this formula implies that there is a relation between these three theories, and it may give some new insights of the connection between gravity and gauge theory.
        \item A special amplitude --- Double partial amplitude
        %Because of the special color structure of this scalar theory, the authors proposed a easy method to compute all scalar tree amplitudes, and then pure Yang-Mills and gravity can also be done using similar methods.
        \item BCJ double copy at tree level
        %In terms of this construction of amplitudes, it is easy to obtain the BCJ double copy relation. It may give some implications for the construcion of nonpermubative BCJ double copy.
        \item Related to other theories, such as EYM, EM, NLSM and so on.
        %In the following paper of these authors, by introducing some special operations which performed on the integrand of CHY formula, they give some relations between other theories.   
    \frametitle{Scattering equations}
    It has benn proposed that there is connection between the scattering data of n massless particles and the n-punctured sphere from a rational map
        k_\mu^a=\frac{1}{2\pi i}\oint_{|z-\sigma_a|}dz\frac{p^\mu(z)}{\prod ^n_{b=1}(z-\sigma_b)}

@@

    \begin{block}{\textcolor{red}{Scattering equations}}
        \begin{equation*}
            \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\qquad a\in \{1,\dots,n\}
        \end{equation*}
    \end{block}
    It has been proved that the number of solutions in any dimension is $\alert{(n-3)!}$, and only \alert{$n-3$} of the equtions are independent, so we can rewrite the scattering equations as following 
    \begin{equation*}
        \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\quad a\in \{4,5,\dots,n\}\quad and\quad  \sigma_1\rightarrow\infty,\sigma_2=0,\sigma_3=1
    \end{equation*}
\end{frame}
\iffalse
\section{CHY Formula}
\begin{frame}{Scattering equations}
    It has benn proposed that there is connection between the scattering data of n massless particles and the n-punctured sphere from a rational map
    \begin{equation*}
        k_\mu^a=\frac{1}{2\pi i}\oint_{|z-\sigma_a|}dz\frac{p^\mu(z)}{\prod ^n_{b=1}(z-\sigma_b)}
    \end{equation*}

    \begin{block}{\textcolor{red}{Scattering equations}}
        \begin{equation*}
            \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\qquad a\in \{1,\dots,n\}
        \end{equation*}
    \end{block}
    It has been proved that the number of solutions in any dimension is $\alert{(n-3)!}$, and only \alert{$n-3$} of the equtions are independent, so we can rewrite the scattering equations as following 
    \begin{equation*}
        \sum_{b\neq a } \frac{s_{ab}}{\sigma_a-\sigma_{b}}=0,\quad a\in \{4,5,\dots,n\}\quad and\quad  \sigma_1\rightarrow\infty,\sigma_2=0,\sigma_3=1
    \end{equation*}
\end{frame}
\fi
\begin{frame}
    \frametitle{Attempt to construct S-matrix --- Towards CHY}
    %Thanks to the excellent properties of scattering equations, it is very tempting to propose that the solutions
    %to scattering equations should be used to construct scattering amplitudes.
    The first two constructed are YM and gravity amplitudes in any dimensions
    \begin{align*}
        M_n^{\mathrm{YM}}(1,2,\dots,n)&=\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)\frac{E_n(\{k,\epsilon,\sigma\})}{\sigma_{12}\dots\sigma_{n1}},\\
        M_n^{\mathrm{gravity}}&=\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)E_n(\{k,\epsilon,\sigma\})^2
    \end{align*}
    The measure is defined as following
    \begin{equation*}
        \prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}{:}=\sigma_{ij}\sigma_{jk}\sigma_{ki}\prod_{a\neq i,j,k}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}
    \end{equation*}
\end{frame}
\begin{frame}
    \frametitle{The form of measure}
    The measure can be written like
    \begin{equation*}
            \boxed{
            \sum_{\{\sigma\}\in\mathrm{solutions}}\frac{(\sigma_{pq}\sigma_{qr}\sigma_{rp})(\sigma_{ij}\sigma_{jk}\sigma_{ki})}{|\Phi|_{pqr}^{ijk}}}
    \end{equation*}
    where the determinant is that of the following Jacobbi matrix
    \begin{equation*}
        \Phi_{ab}\equiv\partial\left(\sum_{c\neq a}\frac{s_{ac}}{\sigma_a-\sigma_c}\right)/\left(\partial\sigma_b\right)=\begin{cases}\frac{s_{ab}}{(\sigma_a-\sigma_b)^2},&a\neq b,\\-\sum_{c\neq a}\Phi_{ac}, &a=b\end{cases}
    \end{equation*}
    Usually we take the notation as following
    \begin{equation*}
        \boxed{
        \det{'}\Phi:=\frac{|\Phi|_{pqr}^{ijk}}{(\sigma_{pq}\sigma_{qr}\sigma_{rp})(\sigma_{ij}\sigma_{jk}\sigma_{ki})}}
    \end{equation*}
\end{frame}

\begin{frame}
    \frametitle{The form of integrand}
    In order to present the explict form of $E_n(\{k,\epsilon,\sigma\})$, first define the following $2n\times2n$ antisymmetric matrix 
    \begin{equation*}
        \Psi=\begin{pmatrix}
            A & -C^T \\
            C & B 
        \end{pmatrix}
    \end{equation*}
    where $A,B$ and $C$ are $n\times n$ matrices, defined as 
    \begin{equation*}
        A_{ab}=\begin{cases}\frac{s_{ab}}{\sigma_a-\sigma_b}&a\neq b,\\0&a=b,\end{cases} \quad 
        B_{ab}=\begin{cases}\frac{\epsilon_a \cdot \epsilon_b}{\sigma_a-\sigma_b}&a\neq b,\\0&a=b, \end{cases} \quad
    \end{equation*}
    \begin{equation*}
        C_{ab}=\begin{cases}\frac{\epsilon_a\cdot k_b}{\sigma_a-\sigma_b}&a\neq b,\\-\sum_{c\neq a}\frac{\epsilon_a\cdot k_c}{\sigma_a-\sigma_c}&a\neq b.\end{cases}
    \end{equation*}
\end{frame}
\begin{frame}
    %The first important observation is that while the Pfaffian of $\Psi$ is 0, but after removing any rows $i,j$ and colums $i,j$
    %with $1\leq i< j\leq n$, the new matrix $\Psi_{ij}^{ij}$ have nonzero Pfaffian and we define the corresponding reduced Pfaffian as 
    The Pfaffian of $\Psi$ is 0, but aftering removing any two rows and colums $i,j$ with $1\leq i< j\leq n$, 
    the new matrix $\Psi_{ij}^{ij}$ have nonzero Pfaffian and we define the corresponding reduced Pfaffian as
    \begin{equation*}
            \boxed{
            \mathrm{Pf}^{\prime}\Psi:=\frac{(-1)^{i+j}}{(\sigma_i-\sigma_j)}\mathrm{Pf}(\Psi_{ij}^{ij})}
    \end{equation*}
    It can be proved that the reduced Pfaffian is invariant under permutaion of \alert{particle labels}.
        M_n^{\mathrm{YM}}(1,2,\dots,n)=\frac{1}{\mathrm{vol\,SL}(2,\mathbb{C})}\int\frac{d^n\sigma}{\sigma_{12}\cdots\sigma_{n1}}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi
    and gravity amplitudes by using KLT construcion
        M_n^{\mathrm{gravity}}=\frac{1}{\mathrm{vol\,SL}(2,\mathbb{C})}\int d^n\sigma\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi\mathrm{Pf}^{\prime}\tilde{\Psi}
        It is easy to discover that the $i$th and $i+n$ th colums become identical, so the determinat and Pfaffian become 0.
        \item \alert{Soft limit}\\
        \mathcal{M}^{(s)} \text{ as \alert{definition of S-matrix for spin s particles}}
    %In order to get more general case, the gravity amplitudes actually can be modified to the product of two different Pfaffians,each with own choice of polariazation vector
    The general case is that we can choose different polariazation vector like 

    \end{tikzpicture}
\end{frame}
\begin{frame}
    \frametitle{Trivalent graph expansion}
    \begin{alertblock}{Proposition}
        The function $m_n^{(0)}(\alpha|\beta)$ computes the sum of all trivalent scalar diagrams which can be regarded as both $\alpha$ color-ordered and $\beta$ color-orded.
    \end{alertblock}
    \pause
    More explicitly, 
    \begin{equation*}
        \boxed{m_n^{(0)}(\alpha|\beta)=(-1)^{n-3+n_{\text{flip}}(\alpha|\beta)}\sum_{g\in\mathcal{T}(\alpha)\cap\mathcal{T}(\beta)}\prod_{e\in E(g)}\frac{1}{s_e}}
\end{equation*}
where the $\text{flip}(\alpha|\beta)$ is defined below, $\mathcal{T}(\alpha)$ and $\mathcal{T}(\beta)$ refer to the set of color-ordered diagrams in $\alpha$ and 
$\beta$ ordering respectively. To make this expression more clear, see the following diagram
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\linewidth]{5.png}
\end{figure}
\end{frame}
\begin{frame}
    We take $m_8^{(0)}(I;18543762)$ as an example to explain how to compute it in an systematic way

    %\begin{itemize}
    %    \item First step, draw a disk with n nodes sitting on the boundary in the ordering $\alpha$, then link the n nodes with a loop of line segments according to
    %          the ording $\beta$. The line segments from $\beta$ split the disk into some polygons, like the graph (b). We need to move the external points of every polygon
    %          to make them have no common edges, like graph (c).
    %    \item Second step, put a point in every polygon, named equivalant vertex, and connect this point to all external points in corresponding area. Lines that connect equivalent 
    %          vertices in two regions with common vertices are called equivalent propagators. The resulting graph is an equivalent Feynman diagram, as shown in Figure (d).
    %\end{itemize}
    \begin{figure}
        \centering
        \includegraphics[width=1\linewidth]{7.png}
    \end{figure}
    In this example, we can obtain 
    \begin{equation*}
        m_8^{(0)}(I|54376218)=(-1)^?\left(\frac{1}{s_{21}}+\frac{1}{s_{18}}\right)\left(\frac{1}{s_{34}}+\frac{1}{s_{45}}\right)\frac{1}{s_{345}s_{812}s_{67}}
    \end{equation*}
    As for the indefinite sign, there is also a procedure to determine it.

    %\begin{itemize}
    %    \item Third step, we can read off the corresponding amplitudes from the equivalent Feynman diagram. 
    %\end{itemize}
    %\begin{itemize}
    %\item First step, determine the orientation of the disk by ordering $\alpha$, and define the loop segments by ordering $\beta$, which also determine the orientation of every polygon.
    %    \item Second step, (1) each polygon with odd number vertices contributes a plus sign if the orientation is the same as disk, and a minus sign oppositely;
    %          (2) each polygon with even number vertices contribute a minus sign; (3) each intersection point contributes a minus sign.
    %\end{itemize}
    \begin{figure}
        \centering
        \includegraphics[width=1\linewidth]{6.png}
    \end{figure}
    The final answer is that
    \begin{equation*}
        m_8^{(0)}(I|54376218)=(-1)^6\left(\frac{1}{s_{21}}+\frac{1}{s_{18}}\right)\left(\frac{1}{s_{34}}+\frac{1}{s_{45}}\right)\frac{1}{s_{345}s_{812}s_{67}}
    \end{equation*}
\end{frame}
\section{Conclusion and Outlook}

\section{Appendix}
\begin{frame}{KLT Relation}
    So-called KLT relation, in the language of field theory, refers to the decomposition of \alert{gravity amplitudes} to \alert{two gauge theory amplitues}. 
    \begin{table}[]
        \resizebox{\textwidth}{!}{
        \begin{tabular}{|l|l|l|l|l|}
        \hline
         \(\mathcal{N}\) & Factors & Supergravity   \\ \hline
         8 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=4SYM\)      &   pure \(\mathcal{N}=8 \)SG             \\ \hline
         6 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=2SYM\)      &   pure \(\mathcal{N}=6 \)SG             \\ \hline
         5 &   \(\mathcal{N}=4SYM\otimes \mathcal{N}=1SYM\)      &   pure \(\mathcal{N}=5 \)SG             \\ \hline
         4 &   \(\mathcal{N}=4SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=4 \)SG,\(n_\nu\)vector multiplets             \\ \hline
         4 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=2SYM\)      &    \(\mathcal{N}=4 \)SG,2 vector multiplets            \\ \hline
         3 &   \(\mathcal{N}=2SYM\otimes \mathcal{N}=1SYM\)      &    \(\mathcal{N}=3 \)SG,1 vector multiplet           \\ \hline
         2 &   \(\mathcal{N}=2SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &    \(\mathcal{N}=2 \)SG,\(n_\nu\) multiplets+1 vector multiplets            \\ \hline
         2 &   \(\mathcal{N}=1SYM\otimes \mathcal{N}=1SYM\)       &    \(\mathcal{N}=2 \)SG ,1 hypermultiplet               \\ \hline
         1 &   \(\mathcal{N}=1SYM\otimes (\mathcal{N}=0YM+n_\nu scalars)\)      &     \(\mathcal{N}=1 \)SG,  \(n_\nu\) vector and 1 chiral multiplet           \\ \hline
        \end{tabular}
        }
        \end{table}
\end{frame}

\appendix
\begin{frame}{KLT Orthogonality}
    $\bullet$ KLT orthogonality is a striking property of the solutions to scattering equations.
    \begin{block}{Proposition 1}
        \begin{equation*}
            \frac{(i,j)}{(i,i)^{\frac12}(j,j)^{\frac12}}=\delta_{ij}
        \end{equation*}
    \end{block}
